\LARGE \bf Matrix Multiplication-Driven Repulsive Fields for 3D Voxel-Based Robotic Manipulator Path Planning

### 2024-03-07 Articles/IROS/root.tex
added field equations

@@

\begin{equation}
w_i = 
\begin{cases} 
	e^{-\frac{\Delta i^2}{2\sigma^2}} / (\sigma \sqrt{2\pi}) & \text{if } \Delta i > 0 \\
	0 & \text{if } \Delta i = 0 \\
	-e^{-\frac{\Delta i^2}{2\sigma^2}} / (\sigma \sqrt{2\pi}) & \text{if } \Delta i < 0 
\end{cases}
\end{equation}

@@

Another distribution we used is mirrored linear, where the $l=\lceil width / 2 \rceil$ is the rounded up half length of the primary axis kernel.

\begin{equation}
	w_i = 
	\begin{cases} 
	 	\frac{l - \Delta i}{l} & \text{if } \Delta i > 0 \\
		0 & \text{if } \Delta i = 0 \\
		\frac{l + \Delta i}{l}& \text{if } \Delta i < 0 
	\end{cases}
\end{equation}

@@

@@

The length of the orthogonal axes influences the peripheral detection range for obstacles. Excessively wide kernels may generate repulsive velocities for objects that are not in the path of the robot, whereas too narrow kernels might only detect obstacles aligned directly with the Cartesian direction in the point of interest. When selecting the width and height of the kernel, we must consider the density of the neighboring points of interest on the robot, ensuring that the \replace{collective fields}{combination of kernels} adequately cover the entire manipulator's surrounding area.

@@

\add{choice of velocity profile (gaussian, linear ... maybe could move this part to implementation / experiments)}

>>>>

\begin{equation}
	S = \sum_{i,j,k} (W \odot A)_{ijk} = \sum_{i}\sum_{j}\sum_{k} w_{\Delta i \Delta j \Delta k} \times  a_{\Delta i \Delta j \Delta k}
\end{equation}

@@

$\Delta i$, $\Delta j$ in $\Delta k$ predstavljajo število celic odmika od centralnega polja matrike, v katerem se nahaja naša točka na agentu v posamezno koordinatno smer.

\begin{equation}
w_{\Delta i} = 
\begin{cases} 
	e^{-\frac{\Delta i^2}{2\sigma^2}} / (\sigma \sqrt{2\pi}) & \text{if } \Delta i > 0 \\
	0 & \text{if } \Delta i = 0 \\
	-e^{-\frac{\Delta i^2}{2\sigma^2}} / (\sigma \sqrt{2\pi}) & \text{if } \Delta i < 0 
\end{cases}
\end{equation}

@@

Another distribution we used is mirrored linear, where the $l=\lfloor width / 2 \rfloor$ is the rounded down half length of the primary axis kernel.

\begin{equation}
	w_{\Delta i} = 
	\begin{cases} 
	 	\frac{l - \Delta i}{l} & \text{if } \Delta i > 0 \\
		0 & \text{if } \Delta i = 0 \\
		\frac{l + \Delta i}{l}& \text{if } \Delta i < 0 
	\end{cases}
\end{equation}

@@

If the matrix would be only 1 field width and height the field would work kind of as ray tracing in each of the main cartesian coordinate directions. Since our need is to detect also obstacles that dont align perfectly along the cartesian direction, it is important that our matrixes have width and height. However as we want bigger repulsive field when the obstacle is head on in the direction than when the obstacle is off the cardinal direction, we propose the following multiplicator, to account for the off direction obstacles.

@@

The length of the orthogonal axes influences the peripheral detection range for obstacles. Excessively wide kernels may generate repulsive velocities for objects that are not in the path of the robot, whereas too narrow kernels might only detect obstacles aligned directly with the Cartesian direction in the point of interest. When selecting the width and height of the kernel, we must consider the density of the neighboring points of interest on the agent, ensuring that the \replace{collective fields}{combination of kernels} adequately cover the entire agent's surrounding area.

For smooth transitions when approaching the obstacles we propose the following sinus based function for the orthagonal axis distributions. The proposed equation is the same for both of the orthagonal matrix directions / axis. That is of course while operating with axis the $r=\lfloor width / 2 \rfloor$ is the rounded down half length of the selected orthagonal axis kernel.

\begin{equation}
	w_{\Delta j} =
	\begin{cases} 
		sin(\left| \Delta j \right| \pi / (2 r)) & \text{if } \Delta j < 0 \text{~or }  \Delta j > 0 \\
		1 & \text{if } \Delta j = 0 \\
	\end{cases}
\end{equation}

Finally we get three matrix kernels, one for each of the three coordinate axis directions by multiplieing weights components for primary and orthagonal axis.

\begin{equation}
	w_{\Delta i \Delta j \Delta k} = w_{\Delta i} * w_{\Delta j} * w_{\Delta k}
\end{equation}

@@
